### 2018-10-29 write-up/semantics/lemmas.tex
Use frac. perm. sub. lemma
Thread through theta-substitution in heaps

@@

Lemma~\ref{stepInC} is the inductive step for this lemma for the $\C{}{}$ case.\\
Need to prove for $\V{}{}$, by induction on $t$ and then index.

@@

>>>>

In the lemma, and for the rest of its proof, $\varsigma = \den{H}{}{\sigma}$.

@@

For the rest of this proof, $\varsigma = \den{H}{}{\sigma}$.\\
Lemma~\ref{stepInC} is the inductive step for this lemma for the $\C{}{}$ case.\\
Need to prove for $\V{}{}$, by induction on $t$ and then index.

@@

\subsection{$\forall e, \sigma, e', \sigma', \theta.\
    \langle \sigma, e \rangle \rightarrow \langle \sigma',  e' \rangle
    \Rightarrow \langle \theta(\sigma), \theta(e) \rangle \rightarrow
    \langle \theta(\sigma') , \theta(e') \rangle$}\label{fracPermSub}

\pf~By induction on $\rightarrow$.
\begin{proof}

    \step{}{\assume{Arbitrary $e, \sigma, e', \sigma', \theta$ such that 
        $\langle \sigma, e \rangle \rightarrow \langle \sigma', e' \rangle$.}}

    \step{}{\suffices{To consider only the following rules which mention
        fractional permission variables.}
        \textsc{Op\_Frac\_Perm}, \textsc{Op\_Share}, \textsc{Op\_Unshare\_(N)Eq}
        and \textsc{Op\_Gemm\_(Mis)Match}.}

    \step{}{\case{\textsc{Op\_Frac\_Perm.}}{Because substitution avoids capture,
        \\ $\langle \theta(\sigma), \theta((\ottkw{fun} fc \rightarrow v) \, [f])
         \rangle \rightarrow \langle \theta(\sigma'\, [fc/f]),
        \theta(v\, [fc/f]) \rangle$.}}

    \step{}{The rest of the cases are parametric in their use of fractional
        permission variables and so will take the same step ater any substitution.}

    \step{}{\textsc{Corollary:}
        If $\langle \sigma \, [fc/f_1], e\, [fc/f_1] \rangle \rightarrow^n
        \langle \sigma_2, e'_2 \rangle$ and
        $\langle \sigma\, [fc/f_2], e \, [fc/f_2] \rangle \rightarrow^n
        \langle \sigma_2, e'_2 \rangle$, then
        $\exists\,\sigma, e'.\ \sigma_1 = \sigma\,[fc/f_1] \wedge
        \sigma_2 = \sigma\,[fc/f_2] \wedge
        e'_1 = e'\,[fc/f_1] \wedge e'_2 = e'\,[fc/f_2]$.}
